# Connection {#connect}

## HTTP connection 

You can start a new connection to your server with the `neo4j_api` object. 

You'll need to call `neo4j_api$new`, with the url (with port specified if any), your user name, and your  password. 

```{r}
library(neo4r)
con <- neo4j_api$new(
  url = "http://localhost:7474",
  user = "neo4j", 
  password = "pouetpouet"
  )
```

If you don't want your password to be included in the script, you can use the `rstudioapi::askForPassword()` function, which will open a little widget asking to interactively enter your password. 

```{r eval = FALSE}
con <- neo4j_api$new(
  url = "http://localhost:7474",
  user = "neo4j", 
  password = rstudioapi::askForPassword()
  )
```

You can then check if you can access to the server by pinging it:

```{r}
con$ping()
```

Which should return 200 if the connexion succeeded. 

## Get informations about the connection :

You'll then be able to get information about the server with: 

```{r}
# Get Neo4J Version
con$get_version()
# List constaints (if any)
con$get_constraints()
# Get a vector of labels (if any)
con$get_labels()
# Get a vector of relationships (if any)
con$get_relationships()
# Get schema 
con$get_schema()
```

