# Convert for common graph packages

### {igraph}

In order to be converted into a graph object:

+ The nodes should be a dataframe with the first column being a series of unique ID, understood as "names" by igraph - these are the ID columns from Neo4J. Other columns are considered attributes.  

+ relationships need a start and an end, *i.e.* startNode and endNode in the Neo4J results. 

Here how to create a graph object from a `{neo4r}` result:

```{r}
G <-"MATCH a=(p:Person {name: 'Tom Hanks'})-[r:ACTED_IN]->(m:Movie) RETURN a;" %>% 
  call_neo4j(con, type = "graph") 

library(dplyr)
library(purrr)
# Create a dataframe with col 1 being the ID, 
# And columns 2 being the names
G$nodes <- G$nodes %>%
  unnest_nodes(what = "properties") %>% 
  # We're extracting the first label of each node, but 
  # this column can also be removed if not needed
  mutate(label = map_chr(label, 1))
head(G$nodes)
```

We then reorder the relationnship table:

```{r}
G$relationships <- G$relationships %>%
  unnest_relationships() %>%
  select(startNode, endNode, type, everything())
head(G$relationships)
```

```{r}
graph_object <- igraph::graph_from_data_frame(
  d = G$relationships, 
  directed = TRUE, 
  vertices = G$nodes
)
plot(graph_object)
```


This can also be used with `{ggraph}` :

```{r}
library(ggraph)
graph_object %>%
  ggraph() + 
  geom_node_label(aes(label = label)) +
  geom_edge_link() + 
  theme_graph()
```

### {visNetwork}

`{visNetwork}` expects the following format : 

#### nodes	
- "id" : id of the node, needed in edges information
- "label" : label of the node
- "group" : group of the node. Groups can be configure with visGroups
- "value" : size of the node
- "title" : tooltip of the node

#### edges	
- "from" : node id of begin of the edge
- "to" : node id of end of the edge
- "label" : label of the edge
- "value" : size of the node
- "title" : tooltip of the node

(from `?visNetwork::visNetwork`).

`visNetwork` is smart enough to transform a list column into several label, so we don't have to worry too much about this one. 

Here's how to convert our `{neo4r}` result:

```{r eval = FALSE}
G <-"MATCH a=(p:Person {name: 'Tom Hanks'})-[r:ACTED_IN]->(m:Movie) RETURN a;" %>% 
  call_neo4j(con, type = "graph") 

# We'll just unnest the properties
G$nodes <- G$nodes %>%
  unnest_nodes(what = "properties")
head(G$nodes)  

# Turn the relationships :
G$relationships <- G$relationships %>%
  unnest_relationships() %>%
  select(from = startNode, to = endNode, label = type)
head(G$relationships)

visNetwork::visNetwork(G$nodes, G$relationships)
```
