# Retrieve data from the API {#retrieve}

The API can be called either from the connection objet, or with the `call_neo4j()` function. 

The `call_neo4j()` function takes several arguments : 

+ `query` : the cypher query
+ `con` : the connexion object 
+ `type` : "rows" or "graph": wether to return the results as a list of results in tibble, or as a graph object (with `$nodes` and `$relationships`)
+ `output` : the output format (R or json) 
+ `include_stats` : whether or not to include the stats about the call 
+ `meta` : wether or not to include the meta arguments of the nodes when calling with "rows"

## "rows" format

The user chooses wether or not to return a list of tibbles when calling the API. You get as many objects as specified in the RETURN cypher statement. 

```{r}
library(magrittr)

'MATCH (tom {name: "Tom Hanks"}) RETURN tom;' %>%
  call_neo4j(con)
```

By default, results are returned as an R list of tibbles. We think this is the more "truthful" way to implement the outputs regarding Neo4J calls. 

For example, when you want to return two nodes types, you'll get two results, in the form of two tibbles (what we've seen just before) - the result is a two elements list with each element being labelled the way it has been specified in the Cypher query. 

Results can also be returned in JSON:

```{r}
'MATCH (cloudAtlas {title: "Cloud Atlas"}) RETURN cloudAtlas;' %>%
  call_neo4j(con, output = "json")
```

Useful for example for writing to a file:

```{r}
tmp <- tempfile(fileext = ".json")
'MATCH (people:Person) RETURN people.name LIMIT 1' %>%
  call_neo4j(con, output = "json") %>%
  write(tmp)
jsonlite::read_json(tmp)
```


If you turn the `type` argument to `"graph"`, you'll get a graph result: 

```{r}
'MATCH (tom:Person {name: "Tom Hanks"})-[act:ACTED_IN]->(tomHanksMovies) RETURN act,tom,tomHanksMovies' %>%
  call_neo4j(con, type = "graph")
```

The result is returned as one node or relationship by row. 

Due to the specific data format of Neo4J, there can be more than one label and property by node and relationship. That's why the results are returned, by design, as a list-dataframe. 

## Parsing results 

We have designed several functions to unnest the output : 

+ `unnest_nodes()`, that can unnest a node dataframe : 

```{r}
res <- 'MATCH (tom:Person {name:"Tom Hanks"})-[a:ACTED_IN]->(m)<-[:ACTED_IN]-(coActors) RETURN m AS acted,coActors.name' %>%
  call_neo4j(con, type = "graph")
unnest_nodes(res$nodes)
```

Note that this function will return `NA` for the properties that aren't in a node. For example here, we have no 'formed' information for the record nodes .

On the long run, and this is not {neo4r} specific but Neo4J related, a good practice is to have a "name" propertie on each node, so this column will be full here.

Also, it is possible to unnest either the properties or the labels : 

```{r}
res %>%
  extract_nodes() %>%
  unnest_nodes(what = "properties")
```

```{r}
res %>%
  extract_nodes() %>%
  unnest_nodes(what = "label")
```

+ `unnest_relationships()`

There is only one nested column in the relationship table, thus the function is quite straightforward : 

```{r}
'MATCH (people:Person)-[relatedTo]-(:Movie {title: "Cloud Atlas"}) RETURN people.name, Type(relatedTo), relatedTo' %>%
  call_neo4j(con, type = "graph") %>%
  extract_relationships() %>%
  unnest_relationships()
```

+ `unnest_graph()`

This function takes a graph results, and does `unnest_nodes` and `unnest_relationships`. 

```{r}
'MATCH (people:Person)-[relatedTo]-(:Movie {title: "Cloud Atlas"}) RETURN people.name, Type(relatedTo), relatedTo' %>%
  call_neo4j(con, type = "graph") %>%
  unnest_graph()
```

### Extraction 

There are two convenient functions to extract nodes and relationships: 

```{r}
'MATCH (bacon:Person {name:"Kevin Bacon"})-[*1..4]-(hollywood) RETURN DISTINCT hollywood' %>%
  call_neo4j(con, type = "graph") %>% 
  extract_nodes()
```

```{r}
'MATCH p=shortestPath(
  (bacon:Person {name:"Kevin Bacon"})-[*]-(meg:Person {name:"Meg Ryan"})
)
RETURN p' %>%
  call_neo4j(con, type = "graph") %>% 
  extract_relationships()
```

