# Sending data to the API {#send}

### Reading and sending a cypher file :

+ `read_cypher` reads a cypher file and returns a tibble of all the calls

```{r}
read_cypher("data-raw/create.cypher")
```

+ `send_cypher` reads a cypher file, and send it the the API. By default, the stats are returned. 

```{r eval = FALSE}
send_cypher("data-raw/constraints.cypher", con)
```


### Sending csv dataframe to Neo4J

The `load_csv` sends an csv from an url to the Neo4J browser. 

The args are : 

+ `on_load` : the code to execute on load 
+ `con` : the connexion object 
+ `url` : the url of the csv to send
+ `header` : wether or not the csv has a header
+ `periodic_commit` : the volume for PERIODIC COMMIT
+ `as` : the AS argument for LOAD CSV
+ `format` : the format of the result 
+ `include_stats` : whether or not to include the stats 
+ `meta` : whether or not to return the meta information

```{r eval = FALSE}
# Create the constraints
call_api("CREATE CONSTRAINT ON (a:artist) ASSERT a.name IS UNIQUE;", con)
call_api("CREATE CONSTRAINT ON (al:album) ASSERT al.name IS UNIQUE;", con)
```

```{r}
# List constaints (if any)
con$get_constraints()
# Create the query that will create the nodes and relationships
on_load_query <- 'MERGE (a:artist { name: csvLine.artist})
MERGE (al:album {name: csvLine.album_name})
MERGE (a) -[:has_recorded] -> (al)  
RETURN a AS artists, al AS albums;'
# Send the csv 
load_csv(url = "https://raw.githubusercontent.com/ThinkR-open/datasets/master/tracks.csv", 
         con = con, header = TRUE, periodic_commit = 50, 
         as = "csvLine", on_load = on_load_query)
```

