# Sending data to the API {#send}

## Reading and sending a cypher file :

+ `read_cypher` reads a cypher file and returns a tibble of all the calls

```{r}
read_cypher("data-raw/create.cypher")
```

+ `send_cypher` reads a cypher file, and send it the the API. By default, the stats are returned. 

```{r eval = FALSE}
send_cypher("data-raw/constraints.cypher", con)
```


## Sending csv to Neo4J

The `load_csv` sends an csv from an url to the Neo4J browser. 

The args are : 

+ `on_load` : the code to execute on load 
+ `con` : the connexion object 
+ `url` : the url of the csv to send
+ `header` : wether or not the csv has a header
+ `periodic_commit` : the volume for PERIODIC COMMIT
+ `as` : the AS argument for LOAD CSV
+ `format` : the format of the result 
+ `include_stats` : whether or not to include the stats 
+ `meta` : whether or not to return the meta information

```{r}
on_load_query <- 'CREATE (n:Product)
  SET n = row,
  n.unitPrice = toFloat(row.unitPrice),
  n.unitsInStock = toInteger(row.unitsInStock), n.unitsOnOrder = toInteger(row.unitsOnOrder),
  n.reorderLevel = toInteger(row.reorderLevel), n.discontinued = (row.discontinued <> "0");'
# Send the csv 
load_csv(url = "http://data.neo4j.com/northwind/products.csv", 
         con = con, header = TRUE, periodic_commit = 50, 
         as = "row", on_load = on_load_query)
```

## Transform elements to cypher queries

+ `vec_to_cypher()` creates a list : 

```{r}
vec_to_cypher(iris[1, 1:3], "Species")
```

+ and `vec_to_cypher_with_var()` creates a cypher call starting with a variable : 

```{r}
vec_to_cypher_with_var(iris[1, 1:3], "Species", a)
```

This can be combined inside a cypher call: 

```{r}
paste("MERGE", vec_to_cypher(iris[1, 1:3], "Species"))
```

